Journal Article Summaries

### 2025-04-08 docs/papers.tex
added nvidia and laplacian smoothing files

    \textbf{Summary:} Uses a neural network classifier to represent the continuous decision boundary of a 3D surface.

    \textbf{Key Points:}
    \begin{itemize}
        \item Existing 3D representations can be broadly categorised into three categories: voxel-based representations, point-based representations, and mesh representations. Point clouds lack connectivity structure of underlying mesh and hence require extra post-processing steps to extract 3D geometry.
        \item Let the occupancy function $o: \R^3 \to \{0,1\}$ denote whether that point is occupied by the object. The paper's occupancy function outputs a probability between 0 and 1 for every point $p\in \R^3$. We want to condition the reconstructed 3D object output on the input $x \in \mathcal X$. Hence, we train an \textit{occupancy network} $f_\theta: \R^3 \times \mathcal X \to [0,1]$, which takes a pair $(p,x)$ and outputs a real number representing the probability of occupancy.
        \item We randomly sample points in the 3D bounding volume of the object. The loss function for a batch $\mathcal B$ is:
        $$\mathcal L_{\mathcal B}^{\text{gen}} = \frac{1}{|\mathcal B|} \sum_{i=1}^{|\mathcal B|} \lr[] {\sum_{j=1}^{K} \mathcal L (f_\theta(p_{ij}, z_i), o_{ij}) + \text{KL}(q_\psi(z | (p_{ij}, o_{ij})_{j=1:K}) \lVert\, p_0(z))}$$ 
        \item Creates a mesh using coarse voxel grid and evaluating occupancy network for cells in this grid. For boundary voxels, we further subdivide them and repeat, until we reach the desired resolution, before applying Marching Cubes.
    \end{itemize}
\end{ArticleSummary}

@@

    \textbf{Key Points:}
    \begin{itemize}
        \item This is unsupervised, so only requires images for training.
        \item Existing pixel-wise loss functions render images from 3D structures but require rasterisation or pixel-wise interpolation commonly, which they claim don't actually contribute to structure learning
        \item DRWR: doesn't require visibility handling, shading, or pixel-wise interpolation.
        \item Loss function: smooth unary loss pulls projection of each 3D point into the foreground (image we're interested in) and binary/pairwise loss pushes each pair of projections lying inside the foreground far away (structure-aware since only considers repulsion once both points appear in foreground). This ensures the entire foreground is covered and prevents clumping.
    \end{itemize}
\end{ArticleSummary}

>>>>

    \textbf{Summary:} Uses a neural network classifier to represent the continuous decision boundary of a 3D surface, enables occupancy to be evaulated at arbitrary resolution.

    \textbf{Key Points:}
    \begin{itemize}
        \item Existing 3D representations can be broadly categorised into three categories: voxel-based representations, point-based representations, and mesh representations. Point clouds lack connectivity structure of underlying mesh and hence require extra post-processing steps to extract 3D geometry.
        \item Let the occupancy function $o: \R^3 \to \{0,1\}$ denote whether that point is occupied by the object. The paper's occupancy function outputs a probability between 0 and 1 for every point $p\in \R^3$. We want to condition the reconstructed 3D object output on the input $x \in \mathcal X$. Hence, we train an \textit{occupancy network} $f_\theta: \R^3 \times \mathcal X \to [0,1]$, which takes a pair $(p,x)$ and outputs a real number representing the probability of occupancy.
        \item We randomly sample points in the 3D bounding volume of the object. The loss function for a batch $\mathcal B$ is:
        $$\mathcal L_{\mathcal B}^{\text{gen}} = \frac{1}{|\mathcal B|} \sum_{i=1}^{|\mathcal B|} \lr[] {\sum_{j=1}^{K} \mathcal L (f_\theta(p_{ij}, z_i), o_{ij}) + \text{KL}(q_\psi(z | (p_{ij}, o_{ij})_{j=1:K}) \lVert\, p_0(z))}$$ 
        \item Creates a mesh using coarse voxel grid and evaluating occupancy network for cells in this grid. For boundary voxels, we further subdivide them and repeat, until we reach the desired resolution, before applying Marching Cubes.
        \item In ShapeNet results, able to construct finer details which get lost in coarser voxel representations.
    \end{itemize}
\end{ArticleSummary}

@@

    \textbf{Key Points:}
    \begin{itemize}
        \item This is unsupervised, so only requires images for training, whereas existing approaches require large amounts of data.
        \item Existing pixel-wise loss functions render images from 3D structures but require rasterisation or pixel-wise interpolation commonly, which they claim don't actually contribute to structure learning
        \item DRWR: doesn't require visibility handling, shading, or pixel-wise interpolation.
        \item Loss function: smooth unary loss pulls projection of each 3D point into the foreground (image we're interested in) and binary/pairwise loss pushes each pair of projections lying inside the foreground far away (structure-aware since only considers repulsion once both points appear in foreground). This ensures the entire foreground is covered and prevents clumping.
        \item Link to my approach: renderers bridge the gap between 3D and 2D by using 2D loss functions on 3D structure, loss functions which are usually defined on RGB pixelvalues or pixel-wise silhouette coverage. Renders predicted 3D structure from specific view angle into an image.
    \end{itemize}
\end{ArticleSummary}
